Supporting Information

### 2018-03-07 SupportingInformation.Rmd
don't know what changed but it is making me commit
sourcing skewness file

<!--Basic setup-->
```{r setup, echo=F}
knitr::opts_chunk$set(echo = TRUE, fig.pos = "H")

@@

source("getcopula.R")
source("OurBiCopSelect.R")
source("FittingCopula_selective_loc.R")
source("aphid_data_calling.R")
source("plankton_north_sea_data_calling.R")
source("NonParamStat.R")
source("copsurrog2d.R")
```

@@

@@

<!--Now create the plot and save it to the results folder-->
```{r plot_soilCN_graphic_approach, echo=F}
x<-seq(from=0.05,to=0.95,by=0.1)
xlimits<-c(0,1)

@@

We also tested statistically for asymmetry of tail dependence, which seems visible in `r table_nums("soilCNcop",display="c")`. 
Results (`r table_nums("soilCN_asym",display="c")`) show that upper-tail dependence was, indeed, significantly stronger than lower-tail dependence in these data.

@@

<!--Shya to add results about skewness of spatial means-->
```{r skewness_count_plot, echo=F, cache=T, cache.extra=list(seed,mtime("ncsurrog.R"),mtime("skewness_multivar_dataset.R"))}
set.seed(seed)
pdf("./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10.pdf")
par(mfrow=c(2,1))
numsurrog<-10000
loclist<-good_loclist(d_allsp=data_aphid_count,sp=10,data_pt_thrs=30)
answer1k<-skewness_testing(ts_matrix=sp_data(sp=10,d_allsp=data_aphid_count),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="kendall")

@@

<!--Shya to add results about skewness of spatial means-->
```{r skewness_ff_plot, echo=F, cache=T, cache.extra=list(seed,mtime("ncsurrog.R"),mtime("skewness_multivar_dataset.R"))}
set.seed(seed)
pdf("./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11.pdf")
par(mfrow=c(2,1))
numsurrog<-10000
loclist<-good_loclist(d_allsp=data_aphid_ff,sp=11,data_pt_thrs=30)

@@

<!--Shya to add results about skewness of spatial means-->
<!--Shya to add results about skewness of spatial means-->
```{r skewness_pns_plot, echo=F, cache=T, cache.extra=list(seed,mtime("ncsurrog.R"),mtime("skewness_multivar_dataset.R"))}
set.seed(seed)
pdf("./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16.pdf")
par(mfrow=c(2,1))
numsurrog<-10000
loclist<-good_loclist(d_allsp=data_plankton_north_sea,sp=16,data_pt_thrs=45)
answer3k<-skewness_testing(ts_matrix=sp_data(sp=16,d_allsp=data_plankton_north_sea),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="kendall")

>>>>

<!--Basic setup-->
```{r setup, echo=F}
knitr::opts_chunk$set(echo = TRUE, fig.pos = "H") #, warning=F)

@@

source("getcopula.R")
source("OurBiCopSelect.R")
source("FittingCopula_selective_loc.R")
source("aphid_data_calling.R")
source("plankton_north_sea_data_calling.R")
source("NonParamStat.R")
source("copsurrog2d.R")
source("TestStats_multivar_dataset.R")
source("skewness_multivar_dataset.R")
```

@@

### Stat-testing of Non-parametric analysis (for limited number of datapoints)
```{r stat_testing_save_result, message=F, warning=F, echo=F, cache=T, cache.extra=list(seed,mtime("TestStats_multivar_dataset.R"))}
set.seed(seed)

resultsloc<-"./Results/stat_results/stat_testing/"
callfn<-coplist_with_params(spearvals=seq(from=0,to=0.9,by=0.1))
coplist<-callfn$coplist
ncores<-3
res_pt35_rankF<-mclapply(X=coplist,FUN=worker,numpts=35,numsims=100,rank=F,mc.cores=ncores)
res_pt35_rankT<-mclapply(X=coplist,FUN=worker,numpts=35,numsims=100,rank=T,mc.cores=ncores)
res_pt1000_rankF<-mclapply(X=coplist,FUN=worker,numpts=1000,numsims=100,rank=F,mc.cores=ncores)
res_pt1000_rankT<-mclapply(X=coplist,FUN=worker,numpts=1000,numsims=100,rank=T,mc.cores=ncores)
save(res_pt35_rankF,res_pt35_rankT,res_pt1000_rankF,res_pt1000_rankT,file=paste(resultsloc,"StatTestNumericResults.RData",sep=''))
```

```{r stat_testing_plot, results='hide', echo=F, cache=T, cache.extra=list(seed,callfn,mtime("StatTestNumericResults.RData"))}
set.seed(seed)
resultsloc<-"./Results/stat_results/stat_testing/"
b<-callfn$paramlist
plotter_stat_testing(res_pt35_rankF,"res_pt35_rankF",b)
plotter_stat_testing(res_pt35_rankT,"res_pt35_rankT",b)
plotter_stat_testing(res_pt1000_rankF,"res_pt1000_rankF",b)
plotter_stat_testing(res_pt1000_rankT,"res_pt1000_rankT",b)
```

<!--Now give the plot a number so it can be refered to-->
```{r stat_testing35,echo=F}
fig_nums("stat_testing35",display=F)
```
![stat_testing_results_datapt_35](./Results/stat_results/stat_testing/res_pt35_rankT.pdf)

```{r stat_testing1000,echo=F}
fig_nums("stat_testing1000",display=F)
```
![stat_testing_results_datapt_1000](./Results/stat_results/stat_testing/res_pt1000_rankT.pdf)

@@

<!--Now create the plot and save it to the results folder-->
```{r plot_soilCN_graphic_approach, results='hide', echo=F}
x<-seq(from=0.05,to=0.95,by=0.1)
xlimits<-c(0,1)

@@

We also tested statistically for asymmetry of tail dependence, which seems visible in `r fig_nums("soilCNcop",display="c")`. 
Results (`r table_nums("soilCNasym",display="c")`) show that upper-tail dependence was, indeed, significantly stronger than lower-tail dependence in these data.

@@

<!--Shya to add results about skewness of spatial means-->
```{r skewness_count_plot, results='hide',echo=F, cache=T, cache.extra=list(seed,mtime("ncsurrog.R"),mtime("skewness_multivar_dataset.R"))}
set.seed(seed)
pdf("./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10.pdf")
par(mfrow=c(2,1))
numsurrog<-10000
loclist<-good_loclist(d_allsp=data_aphid_count,sp=10,data_pt_thrs=30)
answer1k<-skewness_testing(ts_matrix=sp_data(sp=10,d_allsp=data_aphid_count),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="kendall")

@@

<!--Shya to add results about skewness of spatial means-->
```{r skewness_ff_plot, results='hide',echo=F, cache=T, cache.extra=list(seed,mtime("ncsurrog.R"),mtime("skewness_multivar_dataset.R"))}
set.seed(seed)
pdf("./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11.pdf")
par(mfrow=c(2,1))
numsurrog<-10000
loclist<-good_loclist(d_allsp=data_aphid_ff,sp=11,data_pt_thrs=30)

@@

<!--Shya to add results about skewness of spatial means-->
<!--Shya to add results about skewness of spatial means-->
```{r skewness_pns_plot, results='hide', echo=F, cache=T, cache.extra=list(seed,mtime("ncsurrog.R"),mtime("skewness_multivar_dataset.R"))}
set.seed(seed)
pdf("./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16.pdf")
par(mfrow=c(2,1))
numsurrog<-10000
loclist<-good_loclist(d_allsp=data_plankton_north_sea,sp=16,data_pt_thrs=45)
answer3k<-skewness_testing(ts_matrix=sp_data(sp=16,d_allsp=data_plankton_north_sea),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="kendall")
